A Digital Library for Crowds on the Real-Time Social Web

### 2011-05-05 docs/csce_675/paper.tex
Added introduction.

\section{Related Work}
Twitter\footnote{http://www.twitter.com} is a microblogging platform which is
fast gaining popularity\cite{Oreilly:2009} among broad sections of society and
has a global outreach spreading from developed, urban nations like the United
States where it has a high adoption rate \cite{Java:2007}, to developing
countries in parts of Asia and South America.

@@

%When it comes to visualization of the social crowd, a tool which in some ways
%shows similar objectives as us and stands out among the rest is Vizster
%\cite{Heer:2005}. It is a visualization system for which can be used for
%exploration and navigation of the social networks of any scale. The system
%provides facilities to improve the functionalities like discovering people or
%connections which can help in promoting awareness of community structure and
%exposure to information. It maintains a fun element to it while providing these
%given features. It was aimed to provide specific end-users, functionalities
%like situated exploration and visual analysis of big-scale communities. It is
%based on a design of network layouts which have features like supporting visual
%search and analysis, exploring connectivity in large graphs and automatic
%identification and visualization of structures of communities.

%Another related study was on how web-based retrieval from twitter can be used
%as knowledge base \cite{Cheong:2009} which shows that the visualization system
%we try to attempt can be helpful. Marc Cheong et al. in this study tried to
%analyze demographics of the Twitter users and attempted to provide and analyze
%the trend in Twitter into what's going on in the real world. They enabled us to
%understand the underlying characteristics behind the trend setting in Twitter
%and thereby providing a new perspective on the contributors of a trend. They
%used visualization techniques along with artificial intelligence-based data
%mining methods to classify the Twitter messages dealing with the trend topic.

@@

%Some other studies related come from areas like social network visualization,
%short text visualization, progressive disclosure, and user modeling. Considering
%social network visualization , studies like \cite{Boyd:2008} by Boyd et al described features
%of on-line social networking sites and the history of the social networking sites,
%and the changes during their developments.Deeper understanding of the social
%networks can help boost the research in social network visualization. In Moreno's
%following work \cite{Moreno:1953}, he emphasized the use of pictorial representations to map
%social relations and the embedded patterns. He considered people as nodes in the
%network and relations between people as the edges in the network. Laumann et al
%\cite{Laumann:1966} applied computational procedure, multidimensional scaling to locate nodes in
%visualizing network. The authors are also the first to plot the networks in three
%dimensions. Other examples of good visualizations can be Facebook Friend Wheel
%\cite{facebook_wheel} which visualizes a Facebook user's network of friends in a wheel format and
%Trendsmap \cite{trends_map} which plots real time trending topics over two-dimensional (latitude,
%longitude) world map, and you can zoom in to see the trending topics for a specific
%location or an area.

%In the area of short text visualization, studies like \cite{Bishop:2007} tell that these social
%web-sites serve to fulfill their users' desires to interact with and help others.
%The authors also proposed a 3-level framework for understanding why members of online
%communities participate or not. According to the 3-level framework, users make
%comments or short-text post to have their voice be heard. Leggett and Shipman \cite{Leggett:04} 
%proposed and described the characteristic of interactive communication in seven
%dimensions in a similar way to examine characteristics of communication for a
%commenting system like roles,voices,interaction,indirection,history,narrative
%and media. In \cite{Hsu:09}, they tried to understand how an on-line community itself
%perceives the relative quality of its own user-contributed content and further
%used the information to promote valuable opinion from the flood of comments
%that attached to each social object.We compared three different visualization
%approaches including the traditional list view, the quantitative aggregation
%view and the personalized space view. We learned that, to best present massive
%metadata such as user contributed comments to the end user, a personalized
%filtering model is needed and that a 2D space positional layout is desired
%such as in the case of Plurk and Opinion Space systems.

%In the area of progressive disclosure, Phan et al built a prototype of a system
%that visualized packet traces from a computer network \cite{Phan:07} which is similar to
%the problem investigated. They introduced the concept of progressive multiples
%which combines progressive disclosure with small multiples. In Scalability in
%System Management GUIs \cite{Dieberger:06}, the authors use semantic zooming to show information
%about network configuration at various levels of detail, which can tell about
%the way progressive disclosure can be used for system administrators.In An
%Interactive Ambient Visualization for Code Smells \cite{Murphy:10}, the authors describe a
%method for alerting uses about code that may need refactoring. They created a
%plug-in for Eclipse that detected questionable code and alerts the programmer.
%This shows progressive disclosure for software developers.

%Involving user models and visualization into the picture, studies like \cite{Schlungbaum:97} tell
%that the individualization often depends on the user's expectation of the user
%interface which might be adapted or adaptable or adaptive user interface. Papers
%like \cite{Ho:01} explain that the user model selection is crucial for any tool and how
%the visualization can help in the discovering and building knowledge. Data and
%knowledge visualization module of such a system can be used to help the user
%interaction in other modules. This helps in better user interaction experience
%irrespective of which module of the system he/she is interacting with.The user's
%knowledge, preferences, goals etc. are generally included in the user model when
%visualization is concerned in such tools \cite{Henderson}. Also, critical factors like cognitive
%load on the user ought to be considered when such tools are made to ensure
%effectiveness.The identification of target users is also a important factor to be
%considered.Model-based tools like TADEUS can include explicit task and user models
%in their system, over potential to work in integrated user interface development
%environments and support the entire user interface life cycle. Although research
%papers like \cite{Schlungbaum:97}, talk about how different software tools can be used for helping
%the user designers create interfaces with consideration of user models , there have
%been efforts to combine user model with task and domain models to help developers
%in creating and designing user interface \cite{Tran:10}. Systems like DB-USE along with TADEUS
%help us in understanding of how user model can be combined with other models to help
%in creating/designing better user interface for applications which are mainly
%concerned with visualization.

>>>>

In much the same way as web search engines provide instant access to the
\textit{retrospective web} of previously crawled and indexed content, there is
growing excitement over a new generation of applications for monitoring,
analyzing, and distilling information from the \textit{prospective web} of
real-time content that reflects the current activity of the web's participants. As a step towards this vision of a prospective web information platform, this
paper developing a digital library for ``hotspots'' on the real-time social web.
In general, a ``hotspot'' could be defined by the posting and sharing actions of
users in social systems, for example triggered by an offline event (e.g.,
Facebook posts and Tweets in response to a live Presidential debate or a chemical
fire at a nearby refinery) or by an online phenomenon (e.g., reaction to Internet
memes, online discussion). Detecting these hotspots as they arise in real-time and providing a framework for browsing and searching them, is
an important and fundamental building block for enabling new real-time web
applications, applications related to identification and dissemination of
disaster and emergency-related information, among many other emerging social
mining applications.

In Section~\ref{sec:related_work}, we describe some papers that discuss the problem we are interested in and in Section~\ref{sec:crowd_algorithm}, we briefly describe our method to discover crowds. We finally present our architecture in Section~\ref{sec:architecture}.

\section{Related Work}
\label{sec:related_work}
Twitter\footnote{http://www.twitter.com} is a microblogging platform which is
fast gaining popularity\cite{Oreilly:2009} among broad sections of society and
has a global outreach spreading from developed, urban nations like the United
States where it has a high adoption rate \cite{Java:2007}, to developing
countries in parts of Asia and South America.

@@

@@
